Analysing the effect of land-use type on the proportion of scouts

### 2021-10-23 analysis/landuse_effect_prop_scouts.Rmd
added urban and rural joint PLS graph, needs more adding to it and sending to vincent and elli

library(tidyr)
library(dplyr)
library(ggfortify)
library(energy)
library(betareg)
library(plsRbeta)
library(lmtest)
```

@@

>>>>

library(tidyr)
library(dplyr)
library(ggfortify)
library(betareg)
library(plsRbeta)
library(lmtest)
```

@@

# Combining the data

```{r}

joined <- bind_rows(rural_lu, urban_lu)
joined[is.na(joined)] <- 0

joined.pcdata <- joined[, 3:length(joined)]

n <- length(joined$p)
y <- (joined$p * (n - 1) + 0.5) / n
joined.pcdata$p_transform <- y

model <- plsRbeta(
  p_transform ~ .,
  data = joined.pcdata,
  nt = ncol(joined.pcdata) - 1,
  model = "pls-beta"
)

print(model)

plsbetamodel <- betareg(
  prop.scouts ~ Comp_.1 + Comp_.2 + Comp_.3 + Comp_.4,
    plsdata
)

newdat <- data_frame(
  Comp_.1 = seq(-50, 140, 0.1),
  Comp_.2 = seq(-50, 140, 0.1),
  Comp_.3 = seq(-50, 140, 0.1),
  Comp_.4 = seq(-50, 140, 0.1)
)

plotdata <- plsdata
plotdata$p <- joined$p

plotdata$LU = ""
plotdata$LU[1:10] = "Rural"
plotdata$LU[11:20] = "Urban"

ggplot(data = plotdata,
  aes(x = Comp_.1 + Comp_.2 + Comp_.3 + Comp_.4, y = p)) +
  geom_point(aes(colour = LU)) +
  geom_rug(aes(colour = LU)) +
  scale_color_manual(values = c("Rural" = "black", "Urban" = "red")) +
  geom_line(data = newdat, aes(x = Comp_.1 + Comp_.2 + Comp_.3 + Comp_.4, y = fit)) +
  xlim(min(-5.5), max(5.5))

ggplot(data = plotdata,
  aes(x = LU, y = Comp_.1 + Comp_.2 + Comp_.3 + Comp_.4)) +
  geom_boxplot(aes(group = LU))

```
